---
title: "NCAA Football Power Projection Map"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: 'https://github.com/andrewjbe/sports-maps-dashboard'
---

```{r setup, include=FALSE, cache=TRUE}
# TODO: get rid of the superflous libraries, I'm not using all of these
library(flexdashboard)
library(cfbfastR)
library(tidyverse)
library(sf)
library(tigris) #
library(leaflet)
library(RCurl)
library(png) #
library(bslib)
library(bsplus)
library(DT)
library(lwgeom)
library(raster)
library(data.table)
library(plotly) #
library(lubridate)
library(ggthemes)

options(scipen = 999)

# Insert your CFBD API key here (nothing will run otherwise):
# https://saiemgilani.github.io/cfbfastR/reference/register_cfbd.html
# Sys.setenv(CFBD_API_KEY="")

source("keys.R")

ds_teams <- cfbd_team_info(year = year(today())) %>%
  unnest(cols = c(logos)) %>%
  distinct(team_id, .keep_all = TRUE) %>%
  # Fixing team colors / logos / names / etc.
  # Illinois' location is all screwed up for some reason
  mutate(
    latitude = if_else(school == "Illinois", 40.1020, latitude),
    longitude = if_else(school == "Illinois", -88.2272, longitude),
    color = if_else(school == "LSU", "#461D7C", color),
    color = if_else(school == "Iowa", "#FCD116", color),
    color = if_else(school == "SMU", "#354CA1", color),
    color = if_else(school == "TCU", "#ffffff", color),
#    color = if_else(school == "Michigan State", "#ffffff", color),
    color = if_else(school == "Utah", "#CC0000", color),
    color = if_else(school == "UCLA", "#F2A900", color),
    color = if_else(school == "Miami (OH)", "black", color),
    color = if_else(school == "Fresno State", "#13284c", color),
    color = if_else(school == "Wisconsin", "#FFFFFF", color),
    color = if_else(school == "USC", "#990000", color),
    color = if_else(school == "Cincinnati", "#444444", color),
    color = if_else(school == "San Diego State", "#A6192E", color),
    color = if_else(school == "UT San Antonio", "#F15A22", color),
    color = if_else(school == "Pittsburgh", "#FFB81C", color),
    logos = if_else(school == "Oregon", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/2483.png", logos),
    logos = if_else(school == "Oklahoma", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/201.png", logos),
    logos = if_else(school == "Kansas State", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/2306.png", logos),
    logos = if_else(school == "Clemson", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/228.png", logos),
    logos = if_else(school == "Air Force", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/2005.png", logos),
    logos = if_else(school == "Michigan State", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/127.png", logos),
    logos = if_else(school == "Nevada", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/2440.png", logos),
    school = if_else(school == "UT San Antonio", "UTSA", school)
  )

# Creating sf object w/ a point for every stadium location
pnts_sf <- st_as_sf(ds_teams, coords = c("longitude", "latitude"))
st_crs(pnts_sf) <- 4326

# County borders overlay -- saved to RDS to save load time
# counties <- counties(cb = TRUE, resolution = "20m")
# counties <- st_transform(counties, 4326)
# saveRDS(counties, "counties_shape.RDS")

counties <- readRDS("counties_shape.RDS")

# states <- states(cb = TRUE, resolution = "20m")
# states <- st_transform(states, 4326)
# saveRDS(states, "states_shape.RDS")

states <- readRDS("states_shape.RDS")
  
# List of available poll weeks / years; only needs to be run once a year -----------------------------------------
# This has nothing to do with the imperialism map, it's for the interactive power proj. map

# TODO: this needs to be set to run automatically, but only once a year. 

# poll_list_ <- tibble()
# 
# for(i in 2001:year(today()) - 1){
# 
#   t <-  cfbd_rankings(year = i, season_type = "regular") %>%
#   # filter(poll == "AP Top 25" | poll == "Coaches Poll",
#   #        !is.na(points)) %>%
#   dplyr::select(c(week, poll, season_type, rank, school, first_place_votes, points)) %>%
#     mutate(
#       season = i
#     )
# 
#   poll_list_ <- rbind(poll_list_, t)
# 
#   f <- cfbd_rankings(year = i, season_type = "postseason") %>%
#   # filter(poll == "AP Top 25" | poll == "Coaches Poll",
#   #        !is.na(points)) %>%
#   dplyr::select(c(week, poll, season_type, rank, school, first_place_votes, points)) %>%
#     mutate(
#       season = i
#     )
# 
#   poll_list_ <- rbind(poll_list_, f)
# 
#   print(i)
# 
# }
# 
# poll_list <- poll_list_ %>%
#   distinct(week, season, season_type)
# 
# write_csv(poll_list, "poll_list.csv")

poll_list <- read_csv("poll_list.csv")

# Adding this year's polls
poll_list <- poll_list %>%
  rbind(., cfbd_rankings(year = year(today()), season_type = "regular") %>%
          distinct(week, season, season_type) %>%
          mutate(season = year(today())))

```


Imperialism Map {data-navmenu="Imperialism Map"}
=======

Row
------

### Imperialism Map

```{r}

ds_results_ <- cfbd_game_info(year = year(today()), season_type = "both")
max_weeks <- as.numeric(max(ds_results_$week))
ds_results_ <- ds_results_ |>
  mutate(week = if_else(season_type == "postseason", max_weeks + 1, as.numeric(week)))

# Loading in base map
load("old_school_imperialism_base_map-3.Rdata")

counties_grouped.os <- counties_grouped.os %>%
  # Have to change everything here too
  # TODO: replace this with something less cumbersome. Just write a function up top?
  mutate(
    color = if_else(school == "LSU", "#461D7C", color),
    color = if_else(school == "Iowa", "#FCD116", color),
    color = if_else(school == "SMU", "#354CA1", color),
    color = if_else(school == "TCU", "#ffffff", color),
#    color = if_else(school == "Michigan State", "#ffffff", color),
    color = if_else(school == "Utah", "#CC0000", color),
    color = if_else(school == "UCLA", "#F2A900", color),
    color = if_else(school == "Miami (OH)", "black", color),
    color = if_else(school == "Wisconsin", "#FFFFFF", color),
    color = if_else(school == "San Diego State", "#A6192E", color),
    color = if_else(school == "Fresno State", "#13284c", color),
    color = if_else(school == "USC", "#990000", color),
    color = if_else(school == "UT San Antonio", "#F15A22", color),
    color = if_else(school == "Cincinnati", "#444444", color),
    color = if_else(school == "Pittsburgh", "#FFB81C", color),
    logos = if_else(school == "Oregon", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/2483.png", logos),
    logos = if_else(school == "Oklahoma", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/201.png", logos),
    logos = if_else(school == "Kansas State", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/2306.png", logos),
    logos = if_else(school == "Clemson", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/228.png", logos),
    logos = if_else(school == "Air Force", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/2005.png", logos),
    logos = if_else(school == "Nevada", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/2440.png", logos),
    logos = if_else(school == "Michigan State", "https://a.espncdn.com/i/teamlogos/ncaa/500-dark/127.png", logos),
    school = if_else(school == "UT San Antonio", "UTSA", school)
  )

# function to apply the correct colors to each territory 
fill_team <- colorFactor(ds_teams$color, ds_teams$school)

ds_results <- ds_results_ %>%
  filter(!is.na(home_points)) %>%
  mutate(
    winner = if_else(home_points > away_points, home_team, away_team),
    # winner = if_else(winner %in% ds_teams$school, winner, paste(winner, "(FCS)")),
    loser = if_else(home_points < away_points, home_team, away_team)
  ) %>%
  dplyr::select(winner, loser) %>%
  left_join(., ds_teams %>% dplyr::select(school, logos, color, conference) %>% rename(winner = school), by = "winner") %>%
  rename(winner_logos = logos, winner_color = color) %>%
  # Handles FCS upsets; I have to hardcode these in because the FCS teams aren't in the api data
  # TODO: check if they're in there now / find a way to avoid this
  mutate(
    winner_logos = case_when(
      winner == "UC Davis" ~ 
        "https://a.espncdn.com/i/teamlogos/ncaa/500/2502.png",
      winner == "Eastern Washington" ~ 
        "https://a.espncdn.com/combiner/i?img=%2Fi%2Fteamlogos%2Fncaa%2F500%2F2692.png",
      winner == "South Dakota State" ~ 
        "https://a.espncdn.com/i/teamlogos/ncaa/500/79.png",
      winner == "Holy Cross" ~ 
        "https://a.espncdn.com/i/teamlogos/ncaa/500/107.png",
      winner == "East Tennessee State" ~ 
        "https://a.espncdn.com/i/teamlogos/ncaa/500/236.png",
      winner == "Montana" ~ 
        "https://a.espncdn.com/combiner/i?img=%2Fi%2Fteamlogos%2Fncaa%2F500%2F2692.png",
      winner == "Incarnate Word" ~ 
        "https://a.espncdn.com/combiner/i?img=/i/teamlogos/ncaa/500/2377.png",
      TRUE ~ winner_logos
    ),
    # default logo for if the others are missing
    winner_logos = if_else(is.na(winner_logos), "https://www.ncaa.com/modules/custom/casablanca_core/img/sportbanners/football.svg", winner_logos)
  ) %>%
  distinct()

# This is the loop that iterates through each game result and gives the loser's land to the winner
# TODO: ideally I should only have to change the name, then have this point to a different df w/ the logo, color, etc. 
for(i in (1:nrow(ds_results))){

  counties_grouped.os <- counties_grouped.os %>%
    mutate(
      conference = if_else(school == ds_results$loser[i], ds_results$conference[i], conference),
      logos = if_else(school == ds_results$loser[i], ds_results$winner_logos[i], logos),
      school = if_else(school == ds_results$loser[i], ds_results$winner[i], school)
    )
  
  # if(i %% (nrow(ds_results) / 4) == 0){
  #   print(paste0(
  #     round(100 * (i / nrow(ds_results)), 2), "% done...")
  #     )
  # }

}

# FCS hard codes
counties_grouped.os <- counties_grouped.os %>%
  mutate(
    school = case_when(
      school == "UC Davis" ~ "Portland State",
      school == "South Dakota State" ~ "Southern Illinois",
      school == "Montana" ~ "Weber State",
      school == "Eastern Washington" ~ "Weber State",
      school == "East Tennessee State" ~ "Chattanooga",
      school == "Incarnate Word" ~ "McNeese State",
      TRUE ~ school
    ),
    school = if_else(school == "UT San Antonio", "UTSA", school),
    logos = if_else(school == "UTSA", "http://a.espncdn.com/i/teamlogos/ncaa/500/2636.png", logos)
  ) 

# Summary dataframe
counties_sum.os <- counties_grouped.os %>%
  group_by(school) %>%
  summarize(
    n_territories = n(),
    sum_total = sum(sum(sum_total, na.rm = T)),
    sum_land = sum(sum(sum_land, na.rm = T)),
    sum_water = sum(sum(sum_water, na.rm = T)),
    sum_population = sum(sum(total_pop, na.rm = T)),
    sum_n = sum(sum(n, na.rm = T))
    ) %>%
  left_join(ds_teams %>% dplyr::select(school, logos), by = "school") %>%
  distinct()

# function to define logo size; scales with log(territory size)
logoIcons.os <- icons(
  iconUrl = counties_grouped.os$logos,
  iconWidth = (as.numeric(log(st_area(counties_grouped.os))) - 21) * 11,
  iconHeight = (as.numeric(log(st_area(counties_grouped.os))) - 21) * 11
)

# This is the actual map -------------------------------------------------------
leaflet() %>%
  setView(lng = -95.24580, lat = 38.95909, zoom = 4) %>%
  addPolygons(data = counties_grouped.os, 
              smoothFactor = 0.2, 
              color = "white", 
              fillColor = ~fill_team(school), 
              fillOpacity = 0.9, 
              label = ~school, 
              weight = 1, 
              group = "Current Map",
              highlightOptions = highlightOptions(color = 'white', weight = 1, bringToFront = FALSE)
              ) %>%
  addCircleMarkers(data = ds_teams, 
                   label = ~school, 
                   stroke = T, 
                   fillOpacity = 0.8, 
                   weight = 0.75, 
                   color = "black", 
                   fillColor = ~color, 
                   radius = 5, 
                   group = "Toggle School Locations",
                   popup = paste0("<center><img src=", ds_teams$logos, " width = '50' height = '50'>",
                                  "<br><hr><b>", ds_teams$school, "</center>",
                                  "</b><br>", ds_teams$conference,
                                  "<br>Mascot: ", ds_teams$mascot
                   )) %>%
  addMarkers(data = st_centroid(counties_grouped.os), label = ~school, icon = logoIcons.os, group = "Current Map",
             popup = paste0(
               "<center><b>", counties_grouped.os$city, " Territory, home of the ", counties_grouped.os$mascot, "</b><br></center>",
               "<center>Currently Controlled by ", counties_grouped.os$school, "<br></center>",
               "<hr>",
               "Territory Area: ", format(round(counties_grouped.os$sum_land, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
               "Territory Water area: ", format(round(counties_grouped.os$sum_water, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
               "No. of Counties in Territory: ", format(counties_grouped.os$n, nsmall = 1, big.mark = ","), "<br>",
               "Territory Population: ", format(counties_grouped.os$total_pop, big.mark = ",")
             )) %>%
  addPolylines(data = counties,
               color = "black", 
               weight = 0.2, 
               smoothFactor = 0,
               opacity = 1, 
               group = "Toggle County Borders") %>%
  addPolylines(data = states, 
               color = "black",
               weight = 0.4, 
               smoothFactor = 0, 
               opacity = 1, 
               group = "Toggle State Borders") %>%
  addTiles() %>%
  addLayersControl(
    baseGroups = c("Current Map"),
    overlayGroups = c("Toggle School Locations", "Toggle County Borders", "Toggle State Borders"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  hideGroup(c("Toggle School Locations", "Toggle County Borders", "Toggle State Borders"))


```

> This is the CFB "Imperialism Map". The rules are as follows: at the beginning of the season, every county in the US (minus Alaska, which is not home to any FBS teams) was divided amongst the 130 FBS college football teams, with each county going to the team whose stadium is closest to the county's center. From this starting map, the teams gain or lose land based on their performance on the field; every time a game concludes, the loser cedes whatever lands they control to the victor. You can click (or tap on mobile) on team logos to see the name of the "territory", the current owner, the original owner, and a few other stats as well. More stats can be found on the "Stat Explorer" page under the "Imperilaism Map" tab at the top of this page.

Row
-----------------------------------------------------------------------

### Biggest Domain {.no-mobile}

```{r}
top_domain.os <- counties_sum.os %>% slice_max(order_by = sum_total, n = 1, with_ties = F) %>% pull(var = school)

renderValueBox({

  valueBox(
    value = top_domain.os,
    caption = paste0(
      "Biggest Domain: ",
      format(round(counties_sum.os %>% slice_max(order_by = sum_total, n = 1, with_ties = F) %>%
                     pull(var = sum_total), 1), big.mark = ","), " Sq. miles"),
    color = ds_teams %>% filter(school == top_domain.os) %>% pull(var = color)
  )

})
```

### Largest Water Area {.no-mobile}

```{r}
top_water.os <- counties_sum.os %>% slice_max(order_by = sum_water, n = 1, with_ties = F) %>% pull(var = school)

renderValueBox({

  valueBox(
    value = top_water.os,
    caption = paste0(
      "Largest Water Area: ",
      format(round(counties_sum.os %>% slice_max(order_by = sum_water, n = 1, with_ties = F) %>%
                     pull(var = sum_water), 1), big.mark = ","), " Sq. miles"),
    color = ds_teams %>% filter(school == top_water.os) %>% pull(var = color)
  )

})
```

### Most Territories Controlled {.no-mobile}

```{r}
top_territories.os <- counties_sum.os %>% slice_max(order_by = n_territories, n = 1, with_ties = F) %>% pull(var = school)

renderValueBox({

  valueBox(
    value = top_territories.os,
    caption = paste0(
      "Most Territories Controlled: ",
      format(round(counties_sum.os %>% slice_max(order_by = n_territories, n = 1, with_ties = F) %>%
                     pull(var = n_territories), 1), big.mark = ",")),
    color = ds_teams %>% filter(school == top_territories.os) %>% pull(var = color)
  )

})
```

### Most Counties Controlled {.no-mobile}

```{r}
top_counties.os <-  counties_sum.os %>% slice_max(order_by = sum_n, n = 1, with_ties = F) %>% pull(var = school)

renderValueBox({

  valueBox(
    value = top_counties.os,
    caption = paste0(
      "Most Counties Controlled: ",
      format(round(counties_sum.os %>% slice_max(order_by = sum_n, n = 1, with_ties = F) %>%
                     pull(var = sum_n), 1), big.mark = ",")),
    color = ds_teams %>% filter(school == top_counties.os) %>% pull(var = color)
  )

})
```

### Largest Population {.no-mobile}

```{r}
top_pop.os <- counties_sum.os %>% slice_max(order_by = sum_population, n = 1, with_ties = F) %>% pull(var = school)

renderValueBox({

  valueBox(
    value = top_pop.os,
    caption = paste0(
      "Largest Population: ",
      format(round(counties_sum.os %>% slice_max(order_by = sum_population, n = 1, with_ties = F) %>%
                     pull(var = sum_population), 1), big.mark = ","), " people"),
    color = ds_teams %>% filter(school == top_pop.os) %>% pull(var = color)
  )

})


```


Stat Explorer {data-navmenu="Imperialism Map"}
=====================================

Row
------

### Statistics Table

```{r}

renderDataTable({

  DT::datatable(
    data = counties_sum.os %>%
      dplyr::select(c(logos, school, sum_n, sum_land, sum_water, sum_total, sum_population)) %>%
      st_drop_geometry() %>%
      mutate(
        sum_land = round(sum_land, 2),
        sum_water = round(sum_water, 2),
        sum_total = round(sum_total, 2),
        sum_population = round(sum_population, 2),
        logos = paste0("<img src='", logos, "' width='50' height='50'>")
      ) %>%
      rename(
        Team = school,
        'Counties Controlled' = sum_n,
        'Total Land Area (sq. mi.)' = sum_land,
        'Total Water Area (sq. mi.)' = sum_water,
        'Total Territory (sq. mi.)' = sum_total,
        'Total Population' = sum_population
      ),
    rownames = FALSE, options = list(scrollY = 550, pageLength = 100, dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')),
    extensions = 'Buttons',
    escape = FALSE
  ) %>%
  formatRound(c('Total Land Area (sq. mi.)', 'Total Water Area (sq. mi.)', 'Total Territory (sq. mi.)', 'Total Population'), digits = 0)

})

```


Power Projection Map Generator {data-navmenu="Power Projection Maps"}
==================================

Inputs {.sidebar}
----------------------------

---

```{r}

shiny::numericInput(
  inputId = "year_input",
  label = "Season (start year)",
  value = 2021,
  min = 2001,
  max = 2021
  # choices = c(2001:2021)
)

renderUI({
  
  shiny::selectInput(
    inputId = "week_input",
    label = "Week",
    selected = poll_list %>% filter(season == year(today())) %>% slice_max(week, n = 1) %>% pull(var = week),
    choices = poll_list %>% filter(season == input$year_input & season_type == input$type_input) %>% distinct(week) %>% 
      unlist(use.names = F)
)

})
  
shiny::selectInput(
  inputId = "type_input",
  label = "Season Type",
  choices = c("regular", "postseason"),
  selected = "regular"
)

actionButton(
  inputId = "input_execute",
  label = "Generate Map", 
  # class = "btn-primary",
  icon("paper-plane"), 
  style = "color: #fff; background-color: #337ab7; border-color: #2e6da4"
)

```

---

Please note that this button calculates a power projection score for every single county / team combo, so it takes a while to generate the map. 


Row 
-----------------------------------------------------------------------

### Power Projection Map Maker

```{r}

# Creating map ==================================================================
# =================================================================================
  
ds_teams.react <- eventReactive(input$input_execute, {
  
  ds_teams_ <- cfbd_team_info(year = input$year_input) %>%
  unnest(cols = c(logos)) %>%
  distinct(team_id, .keep_all = TRUE) %>%
  # Illinois is all screwed up for some reason
  mutate(
    latitude = if_else(school == "Illinois", 40.1020, latitude),
    longitude = if_else(school == "Illinois", -88.2272, longitude),
    color = if_else(school == "LSU", "#461D7C", color)
  ) 

  ds_rank <- cfbd_rankings(year = input$year_input, season_type = input$type_input) %>%
  filter(poll == if_else(input$year_input <= 2013, "Coaches Poll", "AP Top 25"),
         !is.na(points),
         week == input$week_input) %>%
  dplyr::select(c(week, poll, season_type, rank, school, first_place_votes, points))

  ds_teams <- ds_teams_ %>%
  left_join(., ds_rank) %>%
  filter(!is.na(rank)) %>%
    distinct()

  return(ds_teams)
  
})

# Make this reactive
counties_grouped.react <- eventReactive(input$input_execute, {
  
  withProgress(expr = {
  
pnts_sf <- st_as_sf(ds_teams.react(), coords = c("longitude", "latitude"))
st_crs(pnts_sf) <- 4326

counties <- counties(cb = TRUE, resolution = "20m")
st_crs(counties) <- 4326

counties <- counties %>%
  mutate(
    n = row_number()
  )

setProgress(value = 0, message = "Calculating Power Projection scores...")

closest_ <- list()
for (i in seq_len(nrow(counties))) {
  closest_[[i]] <- pnts_sf[which.max(
    (ds_teams.react()$points) * (1 / sf::st_distance(pnts_sf, counties[i, ]))
    ), ]
#  print(paste0(round(100 * i / nrow(counties), 2), "%"))
  setProgress(value = i / nrow(counties))
}
closest_ <- rbindlist(closest_)

closest_ <- closest_ %>%
  dplyr::select(school, color, logos) %>%
  mutate(
    n = row_number()
  )

counties_ <- left_join(counties, closest_, by = "n")

setProgress(value = 0.99, message = "Adding additional variables...")

# counties_pop <- get_estimates(geography = "county", product = "population") %>%
#   rename(estimate = value)
# write_csv(counties_pop, "counties_pop.csv")

counties_pop <- read_csv("counties_pop.csv")

counties_ <- merge(counties_, counties_pop, by = "GEOID")

counties_ <- counties_ %>%
  rename(
    population = estimate
  ) %>%
  dplyr::select(!variable)

# Removes Alaska
counties_ <- counties_ %>%
  filter(STATEFP != "02",
         STATEFP != "72")

incProgress(amount = 0.2, message = "Knitting final data together...")

counties_grouped <- counties_ %>%
  group_by(school, logos, color) %>%
  summarise(
    n = n(),
    sum_land = sum(ALAND) * 0.000000386102,
    sum_water = sum(AWATER) * 0.000000386102,
    sum_total = sum_land + sum_water,
    total_pop = sum(population)
  ) %>%
  st_cast("MULTIPOLYGON")

counties_grouped <- counties_grouped %>%
  left_join(., ds_teams.react())

}, message = "Beginning map generation...")

return(counties_grouped)

})


# Drawing map ===================================================================
# =================================================================================

renderLeaflet({

  logoIcons <- icons(
  iconUrl = counties_grouped.react()$logos,
  iconWidth = 25, iconHeight = 25
)
  
leaflet() %>%
  setView(lng = -95.24580, lat = 38.95909, zoom = 4) %>%
  addPolygons(data = counties_grouped.react(), smoothFactor = 0.2, weight = 0.8,
              color = ~counties_grouped.react()$color, fillOpacity = 0.8, 
              label = counties_grouped.react()$school,
              highlightOptions = highlightOptions(color = 'white', weight = 1,
                                                  bringToFront = FALSE)) %>%
  addCircleMarkers(data = ds_teams, label = ~school, stroke = T, fillOpacity = 0.8,
                   weight = 0.75, color = "black",
                   fillColor = ~color, radius = 5,
                   popup = paste0("<center><img src=", ds_teams$logos, " width = '50' height = '50'>",
                                  "<br><hr><b>", ds_teams$school, "</center>",
                                  "</b><br>", ds_teams$conference,
                                  "<br>Mascot: ", ds_teams$mascot
                                  )) %>%
  addCircleMarkers(data = counties_grouped.react(), label = "", 
                   lat = counties_grouped.react()$latitude, 
                   lng = counties_grouped.react()$longitude,
                  stroke = F, color = "white", fill = "white", fillOpacity = 0.8, radius = 16) %>%
  addMarkers(data = counties_grouped.react(), 
             label = counties_grouped.react()$school,  
             lat = counties_grouped.react()$latitude, 
             lng = counties_grouped.react()$longitude,
             icon = ~logoIcons,
             popup = paste0(
    "<center><b>", counties_grouped.react()$school, "'s</b> Domain<br></center>",
    "<hr>",
    "No. of AP points: ", format(counties_grouped.react()$points, nsmall = 1, big.mark = ","), "<br>",
    "Current AP Poll Rank: ", format(counties_grouped.react()$rank, nsmall = 1, big.mark = ","), "<br>",
    "<hr>",
    "Total land area: ", format(round(counties_grouped.react()$sum_land, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
    "Total water area: ", format(round(counties_grouped.react()$sum_water, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
    "No. of Counties: ", format(counties_grouped.react()$n, nsmall = 1, big.mark = ","), "<br>",
    "Total Population: ", format(counties_grouped.react()$total_pop, big.mark = ",")),
    ) %>%
  addTiles() 
  # setMaxBounds(lng1 = -130,
  #              lat1 = 20,
  #              lng2 = -65,
  #              lat2 = 55)
  
})

```

> This is the CFB "Power Projection Map". This map displays the results of any AP poll since 2001 (seasons prior to 2015 use the Coaches Poll) with the teams controlling land around their home stadium based on how many points they were awarded in the latest poll. The window above will be blank until you generate a map using the "Generate Map" button; you can enter any season 2001-2021, then select any of the available weeks (including the postseason when available), and click "Generate Map" to see what the college football landscape looked like in that week. Check out Week 13 of 2007 to see a week where Alabama was unranked and Kansas was the #2 team in the nation!


Row
-----------------------------------------------------------------------

### Biggest Domain {.no-mobile}

```{r}

renderValueBox({
  
  val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = school))
  clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = color)
  cap <- paste("Biggest Domain:", format(round(counties_grouped.react() %>% 
                              ungroup() %>% 
                              slice_max(order_by = sum_total, n = 1) %>% 
                              pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  
  valueBox(
    value = val,
    color = clr, 
    caption = cap
  )
  
})

```

### Biggest Water Domain {.no-mobile}

```{r}

renderValueBox({
  
  val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = school))
  clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = color)
  cap <- paste("Biggest Water Domain:", format(round(counties_grouped.react() %>% 
                              ungroup() %>% 
                              slice_max(order_by = sum_water, n = 1) %>% 
                              pull(var = sum_water), 1), nsmall = 1, big.mark = ","), "sq. miles")
  
  valueBox(
    value = val,
    color = clr, 
    caption = cap
  )
  
})
```

<!-- ### Biggest Land Domain {.no-mobile} -->

<!-- ```{r} -->

<!-- renderValueBox({ -->

<!--   val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = school)) -->
<!--   clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = color) -->
<!--   cap <- paste("Biggest Land Domain:", format(round(counties_grouped.react() %>%  -->
<!--                               ungroup() %>%  -->
<!--                               slice_max(order_by = sum_land, n = 1) %>%  -->
<!--                               pull(var = sum_land), 1), nsmall = 1, big.mark = ","), "sq. miles") -->

<!--   valueBox( -->
<!--     value = val, -->
<!--     color = clr,  -->
<!--     caption = cap -->
<!--   ) -->

<!-- }) -->
<!-- ``` -->

### Most Counties Controlled {.no-mobile}

```{r}

renderValueBox({
  
  val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = school))
  clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = color)
  cap <- paste("Most Counties Controlled:", format(round(counties_grouped.react() %>% 
                              ungroup() %>% 
                              slice_max(order_by = n, n = 1) %>% 
                              pull(var = n), 1), nsmall = 1, big.mark = ","), "counties")
  
  valueBox(
    value = val,
    color = clr, 
    caption = cap
  )
  
})
```

### Largest Population {.no-mobile}

```{r}

renderValueBox({
  
  val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = school))
  clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = color)
  cap <- paste("Biggest Population:", format(round(counties_grouped.react() %>% 
                              ungroup() %>% 
                              slice_max(order_by = total_pop, n = 1) %>% 
                              pull(var = total_pop), 1), nsmall = 1, big.mark = ","), "people")
  
  valueBox(
    value = val,
    color = clr, 
    caption = cap
  )
  
})
```



Stat Explorer {data-navmenu="Power Projection Maps"}
=====================================

Row
------

### Past Map Stat Table

```{r}

renderDataTable({
  
    
  DT::datatable(
    data = counties_grouped.react() %>% 
      dplyr::select(c(logos, school, n, sum_land, sum_water, sum_total, total_pop, points, rank)) %>%
      st_drop_geometry() %>%
      mutate(
        sum_land = round(sum_land, 2),
        sum_water = round(sum_water, 2),
        sum_total = round(sum_total, 2),
        total_pop = round(total_pop, 2),
        logos = paste0("<img src='", logos, "' width='50' height='50'>")
      ) %>%
      rename(
        Team = school,
        'Counties Controlled' = n,
        'Total Land Area (sq. mi.)' = sum_land,
        'Total Water Area (sq. mi.)' = sum_water,
        'Total Territory (sq. mi.)' = sum_total,
        'Total Population' = total_pop,
        `Points in That Week's Poll` = points,
        `Rank in That Week's Poll` = rank
      ),
    rownames = FALSE, options = list(scrollY = 550, pageLength = 100, dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')), 
    extensions = 'Buttons',
    escape = FALSE
  ) %>%
  formatRound(c('Total Land Area (sq. mi.)', 'Total Water Area (sq. mi.)', 'Total Territory (sq. mi.)', 'Total Population'), digits = 0)
  
})

```

> This page will be blank until you generate a power projection map from a past season on the "Past Seasons Map Generator" tab.

