---
title: "NCAA Football Power Projection Map"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: 'https://github.com/andrewjbe/sports-maps-dashboard'
---

```{r setup, include=FALSE, cache=TRUE}
library(flexdashboard)
library(cfbfastR)
library(tidyverse)
library(ggimage)
library(sf)
library(tigris)
library(leaflet)
library(RCurl)
library(png)
library(bslib)
library(bsplus)
library(DT)
library(lwgeom)
library(raster)
library(data.table)
library(plotly)
library(lubridate)
library(ggthemes)

options(scipen = 999)

# Sys.setenv(CFBD_API_KEY="")

ds_teams_ <- cfbd_team_info(year = year(today())) %>%
  unnest(cols = c(logos)) %>%
  distinct(team_id, .keep_all = TRUE) %>%
  # Illinois' location is all screwed up for some reason
  mutate(
    latitude = if_else(school == "Illinois", 40.1020, latitude),
    longitude = if_else(school == "Illinois", -88.2272, longitude),
    color = if_else(school == "LSU", "#461D7C", color)
  )

# Make this reactive?
ds_rank <- cfbd_rankings(year = year(today()), season_type = "regular") %>%
  filter(poll == "AP Top 25",
         !is.na(points),
         week == max(week)) %>%
  dplyr::select(c(week, poll, season_type, rank, school, first_place_votes, points))

ds_teams <- ds_teams_ %>%
  left_join(., ds_rank)

pnts_sf <- st_as_sf(ds_teams, coords = c("longitude", "latitude"))
st_crs(pnts_sf) <- 4326

counties <- counties(cb = TRUE, resolution = "20m")
st_crs(counties) <- 4326

counties <- counties %>%
  mutate(
    n = row_number()
  )

closest_ <- list()
for (i in seq_len(nrow(counties))) {
  closest_[[i]] <- pnts_sf[which.max(
    (ds_teams$points) * (1 / sf::st_distance(pnts_sf, counties[i, ]))
    ), ]
  print(paste0(round(100 * i / nrow(counties), 2), "%"))
}
closest_ <- rbindlist(closest_)

closest_ <- closest_ %>%
  dplyr::select(school, color, logos) %>%
  mutate(
    n = row_number()
  )

counties_ <- left_join(counties, closest_, by = "n")

# counties_pop <- get_estimates(geography = "county", product = "population") %>%
#   rename(estimate = value)
# write_csv(counties_pop, "counties_pop.csv")

counties_pop <- read_csv("counties_pop.csv")

counties_ <- merge(counties_, counties_pop, by = "GEOID")

counties_ <- counties_ %>%
  rename(
    population = estimate
  ) %>%
  dplyr::select(!variable)

# Removes Alaska
counties_ <- counties_ %>%
  filter(STATEFP != "02",
         STATEFP != "72")

counties_grouped <- counties_ %>%
  group_by(school, logos, color) %>%
  summarise(
    n = n(),
    sum_land = sum(ALAND) * 0.000000386102,
    sum_water = sum(AWATER) * 0.000000386102,
    sum_total = sum_land + sum_water,
    total_pop = sum(population)
  ) %>%
  st_cast("MULTIPOLYGON")

counties_grouped <- counties_grouped %>%
  left_join(., ds_teams)

  
ds_teams <- pnts_sf %>% 
  mutate(
    intersection = as.integer(st_intersects(geometry, counties_grouped)), 
    current_overlord = if_else(is.na(intersection), '', counties_grouped$school[intersection])
    ) %>%
  dplyr::select(current_overlord, school) %>%
  left_join(ds_teams, ., by = "school")

n_subjects <- ds_teams %>% group_by(current_overlord) %>% summarize(n_capitols = n(), capitol_list = paste(school, collapse = ", ")) %>%
  rename(school = current_overlord)

ds_teams <- ds_teams %>%
  left_join(., n_subjects, by = "school")
  
counties_grouped <- counties_grouped %>%
  left_join(., n_subjects, by = "school")
  
# List of available poll weeks / years

# poll_list_ <- tibble()
# 
# for(i in 2001:year(today()) - 1){
# 
#   t <-  cfbd_rankings(year = i, season_type = "regular") %>%
#   # filter(poll == "AP Top 25" | poll == "Coaches Poll",
#   #        !is.na(points)) %>%
#   dplyr::select(c(week, poll, season_type, rank, school, first_place_votes, points)) %>%
#     mutate(
#       season = i
#     )
# 
#   poll_list_ <- rbind(poll_list_, t)
# 
#   f <- cfbd_rankings(year = i, season_type = "postseason") %>%
#   # filter(poll == "AP Top 25" | poll == "Coaches Poll",
#   #        !is.na(points)) %>%
#   dplyr::select(c(week, poll, season_type, rank, school, first_place_votes, points)) %>%
#     mutate(
#       season = i
#     )
# 
#   poll_list_ <- rbind(poll_list_, f)
# 
#   print(i)
# 
# }
# 
# poll_list <- poll_list_ %>%
#   distinct(week, season, season_type)
# 
# write_csv(poll_list, "poll_list.csv")

poll_list <- read_csv("poll_list.csv")

poll_list <- poll_list %>%
  rbind(., cfbd_rankings(year = year(today()), season_type = "regular") %>%
          distinct(week, season, season_type) %>%
          mutate(season = year(today())))

```

Power Projection Map {data-navmenu="Current Power Projection Map"}
=====================================

Row 
-----------------------------------------------------------------------

### Power Projection Map | `r today()`

```{r}

logoIcons <- icons(
  iconUrl = counties_grouped$logos,
  iconWidth = 25, iconHeight = 25
)

leaflet() %>%
  setView(lng = -95.24580, lat = 38.95909, zoom = 4) %>%
  addPolygons(data = counties_grouped, smoothFactor = 0.2, color = ~color, fillOpacity = 0.8, label = ~school, weight = 0.8,
              highlightOptions = highlightOptions(color = 'white', weight = 1,
                                                  bringToFront = FALSE)) %>%
  addCircleMarkers(data = ds_teams, label = ~school, stroke = T, fillOpacity = 0.8, weight = 0.75, color = "black", fillColor = ~color, radius = 5,
                   popup = paste0("<center><img src=", ds_teams$logos, " width = '50' height = '50'>",
                                  "<br><hr><b>", ds_teams$school, "</center>",
                                  "</b><br>", ds_teams$conference,
                                  "<br>Mascot: ", ds_teams$mascot
                                  )) %>%
  addCircleMarkers(data = counties_grouped, label = "", lat = ~latitude, lng = ~longitude,
                   stroke = F, color = "white", fill = "white", fillOpacity = 0.8, radius = 16) %>%
  addMarkers(data = counties_grouped, label = ~school,  lat = ~latitude, lng = ~longitude,
             popup = paste0(
    "<center><b>", counties_grouped$school, "'s</b> Domain<br></center>",
    "<hr>",
    "No. of AP points: ", format(counties_grouped$points, nsmall = 1, big.mark = ","), "<br>",
    "Current AP Poll Rank: ", format(counties_grouped$rank, nsmall = 1, big.mark = ","), "<br>",
    "<hr>",
    "Total land area: ", format(round(counties_grouped$sum_land, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
    "Total water area: ", format(round(counties_grouped$sum_water, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
    "No. of Counties: ", format(counties_grouped$n, nsmall = 1, big.mark = ","), "<br>",
    "Total Population: ", format(counties_grouped$total_pop, big.mark = ",")
  ), icon = logoIcons) %>%
  addTiles() 
  # setMaxBounds(lng1 = -130,
  #              lat1 = 20,
  #              lng2 = -65,
  #              lat2 = 55)

```

> Each county is "controlled" by the team with the highest "power projection" score relative to that county. This score is equal to schools' total AP Poll votes (in the most recent poll) divided by the distance between the school and the nearest county border, in kilometers. In other words, each county is controlled by the strongest nearby team, with stronger teams having a longer "reach". Data source: https://github.com/saiemgilani/cfbfastR-data

Row
-----------------------------------------------------------------------

### Biggest Domain {.no-mobile}

```{r}
top_domain <- counties_grouped %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = school)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = school)
    ),
    color = ds_teams %>% filter(school == top_domain) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  )
  
})
```

### Biggest Water Domain {.no-mobile}

```{r}
top_water <- counties_grouped %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = school)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = school)
    ),
    color = ds_teams %>% filter(school == top_water) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  )
  
})
```

### CFB Stadiums Controlled {.no-mobile}

```{r}
top_subjects <- n_subjects %>% slice_max(order_by = n_capitols, n = 1, with_ties = FALSE)

renderValueBox({
  
  valueBox(
    paste0(
      top_subjects$school[1]
    ),
    color = ds_teams %>% filter(school == top_subjects$school[1]) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste0(top_subjects$school[1], " currently has the most imperial subjects in their domain (", top_subjects$n_capitols[1], ")." )
  )
  
})
```

### Most Counties Controlled {.no-mobile}

```{r}
top_counties <- counties_grouped %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = school)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = school)
    ),
    color = ds_teams %>% filter(school == top_counties) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = n), 1), nsmall = 1, big.mark = ","), "counties")
  )
  
})
```

### Largest Population {.no-mobile}

```{r}
top_pop <- counties_grouped %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = school)

renderValueBox({

  valueBox(
    paste0(
      counties_grouped %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = school)
    ),
    color = ds_teams %>% filter(school == top_pop) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = total_pop), 1), big.mark = ","), "people")
  )

})
```

Stat Explorer {data-navmenu="Current Power Projection Map"}
=====================================

Row 
--------------

### Power Projection Domain Stats

```{r}
  
  DT::datatable(
    data = counties_grouped %>% 
      dplyr::select(c(logos, school, n, sum_land, sum_water, sum_total, total_pop, points, rank, n_capitols, capitol_list)) %>%
      st_drop_geometry() %>%
      mutate(
        sum_land = round(sum_land, 2),
        sum_water = round(sum_water, 2),
        sum_total = round(sum_total, 2),
        total_pop = round(total_pop, 2),
        logos = paste0("<img src='", logos, "' width='50' height='50'>")
      ) %>%
      rename(
        Team = school,
        'Counties Controlled' = n,
        'Total Land Area (sq. mi.)' = sum_land,
        'Total Water Area (sq. mi.)' = sum_water,
        'Total Territory (sq. mi.)' = sum_total,
        'Total Population' = total_pop,
        `Points in Latest AP Poll` = points,
        `Rank in Latest AP Poll` = rank,
        `No. CFB Stadiums Controlled` = n_capitols,
        `Stadiums Controlled` = capitol_list
      ),
    rownames = FALSE, options = list(scrollY = 550, pageLength = 100, dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')), 
    extensions = 'Buttons',
    escape = FALSE
  ) %>%
  formatRound(c('Total Land Area (sq. mi.)', 'Total Water Area (sq. mi.)', 'Total Territory (sq. mi.)', 'Total Population'), digits = 0)
  

```


Past Seasons Map Generator {data-navmenu="Create Historical Power Projection Maps"}
==================================

Inputs {.sidebar}
----------------------------

---

```{r}

shiny::numericInput(
  inputId = "year_input",
  label = "Season (start year)",
  value = 2021,
  min = 2001,
  max = 2021
  # choices = c(2001:2021)
)

renderUI({
  
  shiny::selectInput(
    inputId = "week_input",
    label = "Week",
    selected = 1,
    choices = poll_list %>% filter(season == input$year_input & season_type == input$type_input) %>% distinct(week) %>% 
      unlist(use.names = F)
)

})
  
shiny::selectInput(
  inputId = "type_input",
  label = "Season Type",
  choices = c("regular", "postseason"),
  selected = "regular"
)

actionButton(
  inputId = "input_execute",
  label = "Generate Map", 
  # class = "btn-primary",
  icon("paper-plane"), 
  style = "color: #fff; background-color: #337ab7; border-color: #2e6da4"
)

```

---

Please note that this button calculates a power projection score for every single county / team combo, so it takes a while to generate the map. 


Row 
-----------------------------------------------------------------------

### Power Projection Map Maker

```{r}

# Creating map ==================================================================
# =================================================================================
  
ds_teams.react <- eventReactive(input$input_execute, {
  
  ds_teams_ <- cfbd_team_info(year = input$year_input) %>%
  unnest(cols = c(logos)) %>%
  distinct(team_id, .keep_all = TRUE) %>%
  # Illinois is all screwed up for some reason
  mutate(
    latitude = if_else(school == "Illinois", 40.1020, latitude),
    longitude = if_else(school == "Illinois", -88.2272, longitude),
    color = if_else(school == "LSU", "#461D7C", color)
  )

  ds_rank <- cfbd_rankings(year = input$year_input, season_type = input$type_input) %>%
  filter(poll == if_else(input$year_input <= 2013, "Coaches Poll", "AP Top 25"),
         !is.na(points),
         week == input$week_input) %>%
  dplyr::select(c(week, poll, season_type, rank, school, first_place_votes, points))

  ds_teams <- ds_teams_ %>%
  left_join(., ds_rank) %>%
  filter(!is.na(rank))

  return(ds_teams)
  
})

# Make this reactive
counties_grouped.react <- eventReactive(input$input_execute, {
  
  withProgress(expr = {
  
pnts_sf <- st_as_sf(ds_teams.react(), coords = c("longitude", "latitude"))
st_crs(pnts_sf) <- 4326

counties <- counties(cb = TRUE, resolution = "20m")
st_crs(counties) <- 4326

counties <- counties %>%
  mutate(
    n = row_number()
  )

setProgress(value = 0, message = "Calculating Power Projection scores...")

closest_ <- list()
for (i in seq_len(nrow(counties))) {
  closest_[[i]] <- pnts_sf[which.max(
    (ds_teams.react()$points) * (1 / sf::st_distance(pnts_sf, counties[i, ]))
    ), ]
  print(paste0(round(100 * i / nrow(counties), 2), "%"))
  setProgress(value = i / nrow(counties))
}
closest_ <- rbindlist(closest_)

closest_ <- closest_ %>%
  dplyr::select(school, color, logos) %>%
  mutate(
    n = row_number()
  )

counties_ <- left_join(counties, closest_, by = "n")

setProgress(value = 0.99, message = "Adding additional variables...")

# counties_pop <- get_estimates(geography = "county", product = "population") %>%
#   rename(estimate = value)
# write_csv(counties_pop, "counties_pop.csv")

counties_pop <- read_csv("counties_pop.csv")

counties_ <- merge(counties_, counties_pop, by = "GEOID")

counties_ <- counties_ %>%
  rename(
    population = estimate
  ) %>%
  dplyr::select(!variable)

# Removes Alaska
counties_ <- counties_ %>%
  filter(STATEFP != "02",
         STATEFP != "72")

incProgress(amount = 0.2, message = "Knitting final data together...")

counties_grouped <- counties_ %>%
  group_by(school, logos, color) %>%
  summarise(
    n = n(),
    sum_land = sum(ALAND) * 0.000000386102,
    sum_water = sum(AWATER) * 0.000000386102,
    sum_total = sum_land + sum_water,
    total_pop = sum(population)
  ) %>%
  st_cast("MULTIPOLYGON")

counties_grouped <- counties_grouped %>%
  left_join(., ds_teams.react())

}, message = "Beginning map generation...")

return(counties_grouped)

})


# Drawing map ===================================================================
# =================================================================================

renderLeaflet({

  logoIcons <- icons(
  iconUrl = counties_grouped.react()$logos,
  iconWidth = 25, iconHeight = 25
)
  
leaflet() %>%
  setView(lng = -95.24580, lat = 38.95909, zoom = 4) %>%
  addPolygons(data = counties_grouped.react(), smoothFactor = 0.2, weight = 0.8,
              color = ~counties_grouped.react()$color, fillOpacity = 0.8, 
              label = counties_grouped.react()$school,
              highlightOptions = highlightOptions(color = 'white', weight = 1,
                                                  bringToFront = FALSE)) %>%
  addCircleMarkers(data = ds_teams, label = ~school, stroke = T, fillOpacity = 0.8,
                   weight = 0.75, color = "black",
                   fillColor = ~color, radius = 5,
                   popup = paste0("<center><img src=", ds_teams$logos, " width = '50' height = '50'>",
                                  "<br><hr><b>", ds_teams$school, "</center>",
                                  "</b><br>", ds_teams$conference,
                                  "<br>Mascot: ", ds_teams$mascot
                                  )) %>%
  addCircleMarkers(data = counties_grouped.react(), label = "", 
                   lat = counties_grouped.react()$latitude, 
                   lng = counties_grouped.react()$longitude,
                  stroke = F, color = "white", fill = "white", fillOpacity = 0.8, radius = 16) %>%
  addMarkers(data = counties_grouped.react(), 
             label = counties_grouped.react()$school,  
             lat = counties_grouped.react()$latitude, 
             lng = counties_grouped.react()$longitude,
             icon = ~logoIcons,
             popup = paste0(
    "<center><b>", counties_grouped.react()$school, "'s</b> Domain<br></center>",
    "<hr>",
    "No. of AP points: ", format(counties_grouped.react()$points, nsmall = 1, big.mark = ","), "<br>",
    "Current AP Poll Rank: ", format(counties_grouped.react()$rank, nsmall = 1, big.mark = ","), "<br>",
    "<hr>",
    "Total land area: ", format(round(counties_grouped.react()$sum_land, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
    "Total water area: ", format(round(counties_grouped.react()$sum_water, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
    "No. of Counties: ", format(counties_grouped.react()$n, nsmall = 1, big.mark = ","), "<br>",
    "Total Population: ", format(counties_grouped.react()$total_pop, big.mark = ",")),
    ) %>%
  addTiles() 
  # setMaxBounds(lng1 = -130,
  #              lat1 = 20,
  #              lng2 = -65,
  #              lat2 = 55)
  
})

```

> This is a power projection map like the one one the main page, showing the map for the season / week entered in the sidebar. Seasons prior to 2015 use Coaches Poll points, and seasons 2015 and onward use AP Poll points. The window above will be blank until you generate a map using the "Generate Map" button.


Row
-----------------------------------------------------------------------

### Biggest Domain {.no-mobile}

```{r}

renderValueBox({
  
  val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = school))
  clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = color)
  cap <- paste("Biggest Domain:", format(round(counties_grouped.react() %>% 
                              ungroup() %>% 
                              slice_max(order_by = sum_total, n = 1) %>% 
                              pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  
  valueBox(
    value = val,
    color = clr, 
    caption = cap
  )
  
})

```

### Biggest Water Domain {.no-mobile}

```{r}

renderValueBox({
  
  val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = school))
  clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = color)
  cap <- paste("Biggest Water Domain:", format(round(counties_grouped.react() %>% 
                              ungroup() %>% 
                              slice_max(order_by = sum_water, n = 1) %>% 
                              pull(var = sum_water), 1), nsmall = 1, big.mark = ","), "sq. miles")
  
  valueBox(
    value = val,
    color = clr, 
    caption = cap
  )
  
})
```

<!-- ### Biggest Land Domain {.no-mobile} -->

<!-- ```{r} -->

<!-- renderValueBox({ -->

<!--   val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = school)) -->
<!--   clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = color) -->
<!--   cap <- paste("Biggest Land Domain:", format(round(counties_grouped.react() %>%  -->
<!--                               ungroup() %>%  -->
<!--                               slice_max(order_by = sum_land, n = 1) %>%  -->
<!--                               pull(var = sum_land), 1), nsmall = 1, big.mark = ","), "sq. miles") -->

<!--   valueBox( -->
<!--     value = val, -->
<!--     color = clr,  -->
<!--     caption = cap -->
<!--   ) -->

<!-- }) -->
<!-- ``` -->

### Most Counties Controlled {.no-mobile}

```{r}

renderValueBox({
  
  val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = school))
  clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = color)
  cap <- paste("Most Counties Controlled:", format(round(counties_grouped.react() %>% 
                              ungroup() %>% 
                              slice_max(order_by = n, n = 1) %>% 
                              pull(var = n), 1), nsmall = 1, big.mark = ","), "counties")
  
  valueBox(
    value = val,
    color = clr, 
    caption = cap
  )
  
})
```

### Largest Population {.no-mobile}

```{r}

renderValueBox({
  
  val <- paste0(counties_grouped.react() %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = school))
  clr <- counties_grouped.react() %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = color)
  cap <- paste("Biggest Population:", format(round(counties_grouped.react() %>% 
                              ungroup() %>% 
                              slice_max(order_by = total_pop, n = 1) %>% 
                              pull(var = total_pop), 1), nsmall = 1, big.mark = ","), "people")
  
  valueBox(
    value = val,
    color = clr, 
    caption = cap
  )
  
})
```



Past Map Stat Explorer {data-navmenu="Create Historical Power Projection Maps"}
=====================================

Row
------

### Past Map Stat Table

```{r}

renderDataTable({
  
    
  DT::datatable(
    data = counties_grouped.react() %>% 
      dplyr::select(c(logos, school, n, sum_land, sum_water, sum_total, total_pop, points, rank)) %>%
      st_drop_geometry() %>%
      mutate(
        sum_land = round(sum_land, 2),
        sum_water = round(sum_water, 2),
        sum_total = round(sum_total, 2),
        total_pop = round(total_pop, 2),
        logos = paste0("<img src='", logos, "' width='50' height='50'>")
      ) %>%
      rename(
        Team = school,
        'Counties Controlled' = n,
        'Total Land Area (sq. mi.)' = sum_land,
        'Total Water Area (sq. mi.)' = sum_water,
        'Total Territory (sq. mi.)' = sum_total,
        'Total Population' = total_pop,
        `Points in That Week's Poll` = points,
        `Rank in That Week's Poll` = rank
      ),
    rownames = FALSE, options = list(scrollY = 550, pageLength = 100, dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')), 
    extensions = 'Buttons',
    escape = FALSE
  ) %>%
  formatRound(c('Total Land Area (sq. mi.)', 'Total Water Area (sq. mi.)', 'Total Territory (sq. mi.)', 'Total Population'), digits = 0)
  
})

```

> This page will be blank until you generate a power projection map from a past season on the "Past Seasons Map Generator" tab.

Old School Imperialism Map {data-navmenu="Old School Imperialism Map"}
=======

Row
------

### Old School Imperialism Map

```{r}

ds_results_ <- cfbd_game_info(year = year(today()))

load("old_school_imperialism_base_map.Rdata")

fill_team <- colorFactor(counties_grouped.os$color, counties_grouped.os$school)


ds_results <- ds_results_ %>%
  filter(!is.na(home_points)) %>%
  mutate(
    winner = if_else(home_points > away_points, home_team, away_team),
    loser = if_else(home_points < away_points, home_team, away_team)
  ) %>%
  dplyr::select(winner, loser)

for(i in (1:nrow(ds_results))){
  
  counties_grouped.os <- counties_grouped.os %>%
    mutate(
      school = if_else(school == ds_results$loser[i], ds_results$winner[i], school)
    )

  }


logoIcons <- icons(
  iconUrl = counties_grouped.os$logos,
  iconWidth = 25, iconHeight = 25
)

leaflet() %>%
  setView(lng = -95.24580, lat = 38.95909, zoom = 4) %>%
  addPolygons(data = counties_grouped.os, smoothFactor = 0.2, color = ~fill_team(school), fillOpacity = 0.9, label = ~school, weight = 0.8,
              highlightOptions = highlightOptions(color = 'white', weight = 1,
                                                  bringToFront = FALSE)) %>%
  addCircleMarkers(data = ds_teams, label = ~school, stroke = T, fillOpacity = 0.8, weight = 0.75, color = "black", fillColor = ~color, radius = 5,
                   popup = paste0("<center><img src=", ds_teams$logos, " width = '50' height = '50'>",
                                  "<br><hr><b>", ds_teams$school, "</center>",
                                  "</b><br>", ds_teams$conference,
                                  "<br>Mascot: ", ds_teams$mascot
                   )) %>%
  # addCircleMarkers(data = counties_grouped.os, label = "", lat = ~latitude, lng = ~longitude,
  #                  stroke = F, color = "white", fill = "white", fillOpacity = 0.8, radius = 16) %>%
  # addMarkers(data = counties_grouped.os, label = ~school,  lat = ~latitude, lng = ~longitude,
  #            popup = paste0(
  #              "<center><b>", counties_grouped.os$school, "'s</b> Domain<br></center>",
  #              "<hr>",
  #              "No. of AP points: ", format(counties_grouped.os$points, nsmall = 1, big.mark = ","), "<br>",
  #              "Current AP Poll Rank: ", format(counties_grouped.os$rank, nsmall = 1, big.mark = ","), "<br>",
  #              "<hr>",
  #              "Total land area: ", format(round(counties_grouped.os$sum_land, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
  #              "Total water area: ", format(round(counties_grouped.os$sum_water, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
  #              "No. of Counties: ", format(counties_grouped.os$n, nsmall = 1, big.mark = ","), "<br>",
  #              "Total Population: ", format(counties_grouped.os$total_pop, big.mark = ",")
  #            ), icon = logoIcons) %>%
  addTiles() 



```

> This is the old school-style imperialism map. Each team starts with the counties closest to it, and then loses all their land to their opponents when defeated. You can hover over each territory to see its current owner (or tap if you're on mobile).

Row
-----------------------------------------------------------------------

### Biggest Domain {.no-mobile}

```{r}
top_domain.os <- counties_grouped.os %>% group_by(school) %>% summarize(sum_total = sum(sum(sum_total, na.rm = T))) %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = school)

renderValueBox({
  
  valueBox(
    paste0(
      top_domain.os
    ),
    color = ds_teams %>% filter(school == top_domain.os) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped.os %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  )
  
})
```

### Biggest Water Domain {.no-mobile}

```{r}
top_water.os <- counties_grouped.os %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = school)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped.os %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = school)
    ),
    color = ds_teams %>% filter(school == top_water.os) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped.os %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  )
  
})
```

### Biggest Land Domain {.no-mobile}

```{r}
top_land.os <- counties_grouped.os %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = school)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped.os %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = school)
    ),
    color = ds_teams %>% filter(school == top_land.os) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped.os %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  )
  
})
```

### Most Counties Controlled {.no-mobile}

```{r}
top_counties.os <- counties_grouped.os %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = school)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped.os %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = school)
    ),
    color = ds_teams %>% filter(school == top_counties.os) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped.os %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = n), 1), nsmall = 1, big.mark = ","), "counties")
  )
  
})
```

### Largest Population {.no-mobile}

```{r}
top_pop.os <- counties_grouped.os %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = school)

renderValueBox({

  valueBox(
    paste0(
      counties_grouped.os %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = school)
    ),
    color = ds_teams %>% filter(school == top_pop.os) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped.os %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = total_pop), 1), big.mark = ","), "people")
  )

})


```



<!-- Past Map Stat Explorer {data-navmenu="Old School Imperialism Map"} -->
<!-- ===================================== -->

<!-- Row -->
<!-- ------ -->

<!-- ### Old School Map Stat Table -->

<!-- ```{r} -->

<!-- renderDataTable({ -->


<!--   DT::datatable( -->
<!--     data = counties_grouped.os %>%  -->
<!--       dplyr::select(c(logos, school, n, sum_land, sum_water, sum_total, total_pop)) %>% -->
<!--       st_drop_geometry() %>% -->
<!--       mutate( -->
<!--         sum_land = round(sum_land, 2), -->
<!--         sum_water = round(sum_water, 2), -->
<!--         sum_total = round(sum_total, 2), -->
<!--         total_pop = round(total_pop, 2), -->
<!--         logos = paste0("<img src='", logos, "' width='50' height='50'>") -->
<!--       ) %>% -->
<!--       rename( -->
<!--         Team = school, -->
<!--         'Counties Controlled' = n, -->
<!--         'Total Land Area (sq. mi.)' = sum_land, -->
<!--         'Total Water Area (sq. mi.)' = sum_water, -->
<!--         'Total Territory (sq. mi.)' = sum_total, -->
<!--         'Total Population' = total_pop -->
<!--       ), -->
<!--     rownames = FALSE, options = list(scrollY = 550, pageLength = 100, dom = 'Bfrtip', -->
<!--     buttons = c('copy', 'csv', 'excel', 'pdf', 'print')),  -->
<!--     extensions = 'Buttons', -->
<!--     escape = FALSE -->
<!--   ) %>% -->
<!--   formatRound(c('Total Land Area (sq. mi.)', 'Total Water Area (sq. mi.)', 'Total Territory (sq. mi.)', 'Total Population'), digits = 0) -->

<!-- }) -->

<!-- ``` -->
