---
title: "NCAA Men's Basketball Maps | 2020-2021"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: 'https://github.com/andrewjbe/sports-maps-dashboard'
---

```{r setup, include=FALSE}
library(flexdashboard)

library(tidyverse)
library(raster)
library(data.table)
library(ggimage)
library(lubridate)
library(ggthemes)
library(sf)
library(tigris)
library(leaflet)
library(RCurl)
library(png)
library(plotly)
library(bslib)
library(bsplus)
library(tidycensus)
library(DT)
library(hoopR)

# ncaa_scale <- espn_mbb_teams() %>%
#   filter(!is.na(color)) %>%
#   mutate(
#     color = paste0("#", color),
#     color2 = if_else(is.na(alternate_color), "#000000", paste0("#", alternate_color))
#   ) %>%
#   dplyr::select(team, color, color2)
#
# write_csv(ncaa_scale, "ncaa_scale.csv")
ncaa_scale <- read_csv("ncaa_scale.csv")

ds <- read_csv("schools_cities_coords_logos_fixed.csv")

ds <- merge(ds, ncaa_scale, by = "team")

# # Need to clean data by hand and fix NAs, this is a stopgap
# # ds <- ds %>%
# #   filter(!is.na(lng),
# #          conference == "Big 12 Conference")
 
# # Power projection idea ================================================
 
ds_kp <- hoopR::kp_pomeroy_ratings(min_year = 2021, max_year = 2021) %>%
  mutate(
    team = str_replace(team, "St.", "State")
  )

ds <- left_join(ds, ds_kp) %>% 
  filter(!is.na(lng))

# ds <- read_csv("dataset.csv")

pnts_sf <- st_as_sf(ds, coords = c("lng", "lat"))
st_crs(pnts_sf) <- 4326

counties <- counties(cb = TRUE, resolution = "20m")
st_crs(counties) <- 4326

counties <- counties %>%
  mutate(
    n = row_number()
  )

closest_ <- list()
for (i in seq_len(nrow(counties))) {
  closest_[[i]] <- pnts_sf[which.max(
    (ds$adj_em - 10) * (1000 / sf::st_distance(pnts_sf, counties[i, ]))
    ), ]
  print(paste0(100 * i / nrow(counties), "%"))
}
closest_ <- rbindlist(closest_)

closest_ <- closest_ %>%
  dplyr::select(team, color, logo) %>%
  mutate(
    n = row_number()
  )

counties_ <- left_join(counties, closest_, by = "n")

var_list <- c("B00001_001")
counties_pop <- get_acs(geography = "county", variables = var_list, year = 2018)

counties_ <- merge(counties_, counties_pop, by = "GEOID")

counties_ <- counties_ %>%
  rename(
    population = estimate
  ) %>%
  dplyr::select(!variable)

# Removes Alaska
counties_ <- counties_ %>%
  filter(STATEFP != "02")

counties_grouped <- counties_ %>%
  group_by(team, logo, color) %>%
  summarise(
    n = n(),
    sum_land = sum(ALAND) * 0.000000386102,
    sum_water = sum(AWATER) * 0.000000386102,
    sum_total = sum_land + sum_water,
    total_pop = sum(population)
  ) %>%
  st_cast("MULTIPOLYGON")

# save(counties_grouped, file = "counties_grouped.RData")

# load("counties_grouped.RData")

# gg <- ggplot() + 
#   geom_sf(data = counties_, size = 0.25, aes(fill = team, text = paste("Current Owner:", team))) +
#   geom_sf(data = counties_grouped, color = "white", fill = NA) +
#   geom_point(data = ds, aes(x = lng, y = lat, fill = team, 
#                             text = paste("Capital:", team)), size = 2, shape = 21) +
#   # geom_label_repel(data = ds %>% filter(adj_em > 0),
#   #            aes(x = lng, y = lat, label = team)) +
#   # geom_point(data = ds %>% slice_max(order_by = adj_em, n = 25), aes(x = lng, y = lat), color = "black", fill = "white", size = 12, shape = 21) +
#   # geom_image(data = ds %>% slice_max(order_by = adj_em, n= 25),
#   #            aes(x = lng, y = lat, image = logo), size = 0.017, asp = 1.5) +
#   coord_sf(xlim = c(-128, -67), ylim = c(30, 45)) +
#   scale_fill_manual(breaks = ncaa_scale$team, values = ncaa_scale$color) +
#   scale_color_manual(breaks = ncaa_scale$team, values = ncaa_scale$color2) +
#   guides(fill = "none", color = "none") +
#   theme_map() +
#   theme(legend.position = 'none')

# counties_ %>%
#   group_by(team) %>%
#   summarize(
#     total_area = sum(ALAND + AWATER)
#   ) %>%
#   slice_max(order_by = total_area, n = 10)
```

Power Projection Map
============================

## Row

### Power Projection Map

```{r}

fill_team <- colorFactor(counties_grouped$color, counties_grouped$team)

logoIcons <- icons(
  iconUrl = counties_grouped$logo,
  iconWidth = 20, iconHeight = 20
)

leaflet() %>%
  setView(lng = -95.24580, lat = 38.95909, zoom = 4) %>%
  addPolygons(data = counties_grouped, smoothFactor = 0.2, color = ~fill_team(team), fillOpacity = 0.8, label = ~team,
              highlightOptions = highlightOptions(color = 'white', weight = 1, 
                                                  bringToFront = FALSE)) %>%
  addCircleMarkers(data = ds, label = ~team, stroke = T, fillOpacity = 0.8, weight = 0.75, color = "black", fillColor = ~color, radius = 5, 
                   popup = paste0("<center><img src=", ds$logo, " width = '50' height = '50'></center>", 
                                  "<br><hr><b>", ds$display_name,
                                  "</b><br>", ds$conference,
                                  "<br>W/L Rate: ", ds$w_l,
                                  "<br>Adj. EM: ", ds$adj_em, " (Rank: ", ds$rk, ")",
                                  "<br>Adj. O: ", ds$adj_o, " (Rank: ", ds$adj_o_rk, ")",
                                  "<br>Adj. D: ", ds$adj_d, " (Rank: ", ds$adj_d_rk, ")"
                                  )) %>%
  addCircleMarkers(data = st_centroid(counties_grouped), label = "", 
                   stroke = F, color = "white", fill = "white", fillOpacity = 1) %>%
  addMarkers(data = st_centroid(counties_grouped), label = ~team, popup = paste0(
    "<center><b>", counties_grouped$team, "'s</b> Domain<br></center>",
    "<hr>",
    "Total land area: ", format(round(counties_grouped$sum_land, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
    "Total water area: ", format(round(counties_grouped$sum_water, 1), nsmall = 1, big.mark = ","), " sq. miles<br>",
    "No. of Counties: ", format(counties_grouped$n, nsmall = 1, big.mark = ","), "<br>",
    "Total Population: ", format(counties_grouped$total_pop, big.mark = ",")
  ),
             icon = logoIcons) %>%
  addTiles() %>%
  setMaxBounds(lng1 = -130,
               lat1 = 25,
               lng2 = -65,
               lat2 = 50)
  
```

> Each county is "controlled" by the school with the highest "power projection" score relative to that county. This score is equal to schools' Kenpom Adj. Efficiency Margin (minimum +10) multiplied by the distance between the school and the nearest county border, in kilometers. In other words, each county is controlled by the strongest nearby team, with stronger teams having a longer "reach". Data source: [Kenpom.com](https://kenpom.com/)

## Row

### Biggest Domain {.no-mobile}

```{r}
top_domain <- counties_grouped %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = team)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = team)
    ),
    color = ncaa_scale %>% filter(team == top_domain) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped %>% ungroup() %>% slice_max(order_by = sum_total, n = 1) %>% pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  )
  
})
```

### Biggest Water Domain {.no-mobile}

```{r}
top_water <- counties_grouped %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = team)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = team)
    ),
    color = ncaa_scale %>% filter(team == top_water) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped %>% ungroup() %>% slice_max(order_by = sum_water, n = 1) %>% pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  )
  
})
```

### Biggest Land Domain {.no-mobile}

```{r}
top_land <- counties_grouped %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = team)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = team)
    ),
    color = ncaa_scale %>% filter(team == top_land) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped %>% ungroup() %>% slice_max(order_by = sum_land, n = 1) %>% pull(var = sum_total), 1), nsmall = 1, big.mark = ","), "sq. miles")
  )
  
})
```

### Most Counties Controlled {.no-mobile}

```{r}
top_counties <- counties_grouped %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = team)

renderValueBox({
  
  valueBox(
    paste0(
      counties_grouped %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = team)
    ),
    color = ncaa_scale %>% filter(team == top_counties) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped %>% ungroup() %>% slice_max(order_by = n, n = 1) %>% pull(var = n), 1), nsmall = 1, big.mark = ","), "counties")
  )
  
})
```

### Largest Population {.no-mobile}

```{r}
top_pop <- counties_grouped %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = team)

renderValueBox({

  valueBox(
    paste0(
      counties_grouped %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = team)
    ),
    color = ncaa_scale %>% filter(team == top_pop) %>% pull(var = color)
  ) %>% bs_embed_tooltip(
    title = paste(format(round(counties_grouped %>% ungroup() %>% slice_max(order_by = total_pop, n = 1) %>% pull(var = total_pop), 1), big.mark = ","), "people")
  )

})
```

Power Projection Stats 
=====================================

Row {.tabset}
--------------

### Power Projection Stat Explorer

```{r}
DT::renderDataTable({
  
  DT::datatable(
    data = counties_grouped %>% 
      dplyr::select(c(logo, team, n, sum_land, sum_water, sum_total, total_pop)) %>%
      st_drop_geometry() %>%
      mutate(
        sum_land = round(sum_land, 2),
        sum_water = round(sum_water, 2),
        sum_total = round(sum_total, 2),
        total_pop = round(total_pop, 2),
        logo = paste0("<img src='", logo, "' width='50' height='50'>")
      ) %>%
      rename(
        Team = team,
        'Counties Controlled' = n,
        'Total Land Area (sq. mi.)' = sum_land,
        'Total Water Area (sq. mi.)' = sum_water,
        'Total Territory (sq. mi.)' = sum_total,
        'Total Population' = total_pop
      ),
    rownames = FALSE, options = list(scrollY = 550, pageLength = 100, dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')), 
    extensions = 'Buttons',
    escape = FALSE
  ) %>%
  formatRound(c('Total Land Area (sq. mi.)', 'Total Water Area (sq. mi.)', 'Total Territory (sq. mi.)', 'Total Population'), digits = 0)
  
})

```

### Team Stat Explorer

```{r}
DT::renderDataTable({
  
  DT::datatable(
    data = ds %>% 
      dplyr::select(c(logo, display_name, mascot, conference, w_l, adj_em)) %>%
      mutate(
        logo = paste0("<img src='", logo, "' width='50' height='50'>")
      ) %>%
      rename(
        Logo = logo,
        Team = display_name,
        Mascot = mascot,
        Conference = conference,
        Record = w_l,
        `Kenpom Adj. EM` = adj_em
      ),
    rownames = FALSE, options = list(scrollY = 550, pageLength = 50, dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')), 
    extensions = 'Buttons',
    escape = FALSE
  ) 
})

```

AP Top 10 Over Time
================================

### AP Top 10 Over Time

```{r}

# ds_ap <- read_csv("2021_ap25.csv") %>%
#   pivot_longer(cols = !c(School, Conf), names_to = "Week") %>%
#   mutate(
#     value = as.numeric(value),
#     Week = as.numeric(Week)
#   ) %>%
#   rename(team = School)
# 
# ds_teams <- hoopR::espn_mbb_teams()
# 
# ds_ap <- merge(ds_ap, ds_teams, by = "team")
# 
# ds_ap_10 <- ds_ap %>%
#   mutate(
#     value = if_else(value > 10 | is.na(value), 11, value),
#     short_name = str_replace(short_name, "State", "St."),
#     team = as.factor(team)
#   ) 
# 
# write_csv(ds_ap_10, "ds_ap_10.csv")

ds_ap_10 <- read_csv("ds_ap_10.csv")

p_ap25 <- ds_ap_10 %>%
ggplot(., aes(x = Week, y = value, color = team, 
              text = paste0("Team: ", team, "<br>",
                            "Week: ", Week, "<br>",
                            "Rank: ", value)
              )) +
    geom_line(aes(group = team), size = 2, alpha = 0.3) +
    geom_point(size = 6) +
#    geom_image(aes(image = logo)) + # Not implemented in plotly :(
    geom_text(aes(label = short_name, text = ""), color = "black", nudge_y = 0.3) +
    geom_text(aes(label = paste0("#", value), text = ""), color = "white") +
  theme_clean() +
    theme(legend.position = "none") +
    coord_cartesian(ylim = c(10, 1)) +
    scale_y_reverse(breaks = 1:10) +
    scale_color_manual(breaks = ncaa_scale$team, values = ncaa_scale$color) +
    scale_x_continuous(breaks = 1:17) +
    labs(y = NULL) +
    theme(axis.ticks = element_blank(),
          panel.grid = element_blank(),
          panel.border = element_blank())


ggplotly(p_ap25, tooltip = "text")

```



<!-- Closest Undefeated Team -->
<!-- ================================ -->

<!-- ```{r} -->

<!-- ``` -->

<!-- Imperialism Map -->
<!-- ================================ -->

<!-- ```{r} -->

<!-- ``` -->
